---

title       : Stock Loader
subtitle    : Easy chart Downloader
author      : Bassell Deeb
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : standalone # {standalone, draft}
knit        : slidify::knit2slides

---


## What's App!

Here is the Stock loader an easy app to download and visualize Stocks on your computer
The following slides contain

> 1. How to use it
> 2. How to make predictions
> 3. Download content


This app is very intuitive to use. Simply choose the Symbol you want to visualize.
Add a time period and indicators to plan your strategy.
Finally make predictions to see if your strategy aligns with a predictive model.



---

## How to use it 

Choose one of the Symbols in the of the Dow Jones and choose a time period from the left hand side. A graph like this will show up

```{r echo = F, results = 'asis', message= FALSE, verbose = FALSE, warning= FALSE}
require(quantmod)
getSymbols('YHOO')
chartSeries(YHOO, theme = 'white')
```

---

## How to use it 2

Click on the checkboxes to add indicators and add it directly to the graph. Also choose one of the different options to see the graph using candlesticks, bars, lines (close)...

```{r echo = F, results = 'asis', message= FALSE, verbose = FALSE, warning= FALSE}
require(quantmod)
getSymbols('YHOO')
chartSeries(YHOO, theme = 'white')
addRSI()
addSMA()
```

---

## Make Predictions
Click on the prediction tab to make predictions. Use the slider on the bottom left side to choose the number of periods (days) to make your forecast on.

```{r echo = F, results = 'asis', message= FALSE, verbose = FALSE, warning= FALSE}
require(quantmod)
getSymbols('YHOO')
chartSeries(Next(YHOO, k = 10), theme = 'white')
```

---

## Download Content
Finally click on Download button to download the data of the stock to make your own analysis in csv format!! Good Luck!


---

